A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-06-02 draft/paper2.tex
Add Komiyama-san to author list
Starts from Jenny's edit

    \song{This is the old version, need works}
    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter halos 
    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
    questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

@@

    \song{Need a much shorter version of this}
%% ------------------------------------------------------------------------------------ %%

@@

    The \rbcg{} sample is less affected by completeness because we can utilize 
    photo-$z$s from \redm{}. 
    However, the completeness of the \nbcg{} sample is still limited by the 
    availability of spec-$z$s from BOSS.

@@

        \item We match the two samples according to \mtot{}. 
            We select galaxies from \rbcg{} with $11.6 < $\logmtot{} $<11.9$ 
            (median \logmtot{} ${\sim} 11.74$). 
            There are 45 \rbcg{} galaxies in this range. 
            We then match this distribution by drawing galaxies from \nbcg{}. 
            There are 229 unique \nbcg{} galaxies in the matched sample. 
            In this \mtot{} range, 100 kpc corresponds to 5-8 times the effective radius 
            and \mtot{} is a good proxy of total stellar mass.

       \item We match the two samples according to \minn{}. 
           We select galaxies from \rbcg{} with $11.2 < $\logminn{}$ < 11.6$ 
            (median \logminn{}${\sim} 11.36$).
            For the 56 galaxies from the \rbcg{} sample, we achieve excellent matches
            in \minn{} and redshift using 375 \nbcg{} galaxies.
            Motivated by recent observations and simulations, we use \minn{} as the 
            proxy of the \mstar{} of the ``in-situ'' component.
            We will discuss more about this assumption in 
            Section~\ref{sec:discussion}.

    \end{itemize}

>>>>

    \jenny{Here is a suggested shorter introduction.}   
    One of the most intriguing observations of high-redshift galaxies from the last decade has 
    been the dramatic size growth in massive quiescent galaxies 
    \citep{Trujillo2006,vanDokkum2008,Damjanov2009,Cimatti2008} of factors of $2-4$ from $z \approx 2$ to the present. 
    These observations have led to a two-phase picture of galaxy growth,
    in which galaxies dissipatively form a central compact region and then their envelope grows around 
    them via dry merging \citep[e.g,][]{Naab2006, Khochfar2006,Oser2010, Oser2012}, which allows for 
    dramatic growth at late times. 
    There is likely also a contribution from progenitor bias, in which larger galaxies become quiescent 
    later \citep[e.g.,][]{Newman2012,XX}.

	There have been a number of papers testing the two-phase picture observationally at low redshift, 
    looking at the light profiles \citep{Huang2013a,Huang2013b,Oh2017}, color gradients (), 
    and stellar population gradients \citep[e.g.,][]{}. The observations are generically consistent with the 
    two-phase model. However, to really test this picture requires highly sensitive observations extending 
    beyond 10 kpc to truly probe the material accreted at late times \citep[Illustris paper here?][]{}. The surface 
    brightness falls rapidly in the outer parts of elliptical galaxies, making such observations very challenging. In 
    \citet[][; Paper I hereafter]{Huanetal2017}, we showed that the Hyper-Suprime Camera Survey {\bf CITE} allows us 
    to derive robust surface brightness profiles for {\it individual} galaxies out to 100 kpc.

    In Paper I, we exploited this sensitivity to verify that the fraction of accreted mass residing in an extended
    envelope is a function of the mass of the galaxy. Another unexplored issue is the extent to which, at fixed stellar 
    mass, the accreted fraction depends on the surrounding halo mass. According to this two-phase formation 
    scenario, the late time growth of massive ETGs is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A natural prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''. In this paper, we use our 
    large sample of early-type galaxies, along with halo masses from RedMapper \citep{}, to explore how the mass in
    extended stellar envelopes depends on halo mass. 
    Paper proceeds as follows: XXX.

    \song{This is the old version, needs work}
    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter halos 
    and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many open 
    questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies (ETGs) 
    undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk instabilities 
    or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the so-called 
    ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphologies 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

@@

    \song{Need a much shorter version of HSC data summar here.}

    %    The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.\alexie{Not sure this is important here.}

    \jenny{Here is an attempt to include all the things we really need here.}
    Our sample selection is described in detail in Paper I. Here we include a short summary for completeness. 
    We focus on early-type galaxies with $0.3<z<0.5$ and stellar mass $M_*>10^{11.5}$~\msun. 
    The redshift range includes a large enough volume to have good statistics at the high-mass end, while 
    the stellar mass limit is set by our photometric incompleteness. HSC-identified objects are cross-matched 
    with the spectroscopic and photometric samples from redMapper \citep{Rykoff2014}. Stellar masses are estimated 
    using stellar population synthesis modeling of the broad-band photometry, and then the mass limit is 
    imposed. Using comparisons with published mass functions, we demonstrate that we are complete 
    to $M_*>10^{11.5}$~\msun\ over the full redshift range.

    Finally, here we wish to focus on galaxies that live at the centers of their dark matter halos. 
    We utilize the group information 
    in redMapper v5.10 \citep{Rykoff2014,Rozo2015b} to identify central galaxies. We use the 
    relation between richness $\lambda$ and stellar mass to select groups with 
    $\lambda>30$ or $M_{\rm halo}>10^{14.2}$~\msun\ \citep[e.g.,][]{simetetal2016}. This limit is chosen 
    to mitigate incompleteness at the high end of our redshift window. We then identify the 
    central galaxy to have $P_{\rm CEN}>0.7$. We will refer to this sample of 164 central galaxies as \rbcg{}. The median 
    richness of the sample is $\lambda \approx 41$ ($M_* \approx 2.2 \times 10^{14}$~\msun), and there are 
    only 44 central galaxies in clusters with $\lambda>0.5$ ($M_* > 10^{15}$~\msun). We build a complementary 
    sample of central galaxies in lower-mass halos by calculating the radius of each group with 
    $\lambda>20$ \citep{Diemer2015} and 
    then excluding galaxies within a cylinder around each group, with the thickness of the cylinder broadened to include 
    photo-z uncertainty. The sample of {\bf XX} central galaxies living in halos with $M_* < 10^{14}$~\msun\ will 
    be called \nbcg{}.

@@

@@
